---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(binomialConvolution)
library(plotly)
set.seed(42)
```

A binomial convolution distribution or simply $BC(\mathbf{M}, \mathbf{p})$, where $\mathbf{M} = [M_1, \cdots, M_J]$ and $\mathbf{p} = [p_1, \cdots, p_J]$ is the distribution of a sum of a series of independently but not necessarily identically distributed binomial random variables. In other words, $Y \sim BC(\mathbf{M}, \mathbf{p})$ iff $Y = \sum_{j=1}^J X_j$, where $X_j \sim Binomial(M_j, p_j)$. 

## Simulation

Before we dive into the details, let's first simulate some BC RVs to see what they look like.

```{r}
N = 1000
n_trials = c(10, 20, 30)
success_probs = c(0.1, 0.2, 0.3)
J = length(n_trials)
Y = numeric(N)
for(n in 1 : N)
{
  temp = 0
  for(j in 1 : J)
  {
    temp = temp + rbinom(n=1, 
                         size=n_trials[j],
                         prob=success_probs[j])
  }
  Y[n] = temp
}
```

We have implemented this function (of course in a more efficient way) in our package. To simulate, use the following

```{r}
Y1 = simulate_binomial_convolution(n_samples=N,
                                   n_trials=n_trials,
                                   success_probs=success_probs)
```

```{r, echo=FALSE, fig.show='hold',out.width="49%", out.height="49%"}
par(mar = c(4, 4, .1, .1))
hist(Y)
hist(Y1)
```

## Generating Functions



